A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-24 paper/ms.tex
update ms; consider slope quartile phasedlc
Co-authored-by: adamkraus <alk@astro.as.utexas.edu>

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Further
observations of spectroscopic transits could yield a quantification of
the stellar obliquity, and would confirm or refute the expected
prograde orbital geometry.  Similarly, transit spectroscopy aimed at
detecting atmospheric outflows could yield insight into the
evolutionary state of the atmosphere \citep[{\it
e.g.},][]{ehrenreich_giant_2015,spake_helium_2018,vissapragada_2020}.
Observations aimed at quantifying the amount of high-energy
irradiation incident on the planet would also help in clarifying the
expected outflow rate \citep[{\it e.g.},][]{poppenhaeger_2021}.
Finally, a challenging but informative quantity to measure would be
the planet's mass.  This might be possible through a high-cadence
multi-color radial velocity campaign, or through long-term monitoring
of the transit times and durations.  Measured at sufficient precision,
the mass could yield constraints on both the planet's composition and
its initial entropy \citep{owen_constraining_2020}.

Separately, the Kepler data may yet contain additional information.
For instance, one possible explanation for the transit asymmetry shown
in Figure~\ref{fig:lc} is that of a dusty asymmetric outflow.  Other
possible explanations such as favored longitudes for starspot
crossings seem strained, for reasons discussed in
Appendix~\ref{app:gptransit}.  Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also roughly consistent with predictions
\citep{wang_dai_2019}.  Beyond the planetary transits,
Appendix~\ref{app:flare} highlights a separate oddity in the Kepler
data, in the arrival time distribution of stellar flares.  We
encourage its exploration by investigators more versed in the topic
than ourselves.

@@

\subsection{Long Cadence Data}
\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.64\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Transit model residuals through time (binned by Kepler quarter)}.  
    {\it Left:}
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  Black points are binned to 20
    minute intervals.  The 2-$\sigma$ model uncertainties and the
    maximum {\it a posteriori} model are shown as the faint purple
    band, and the dark purple line.
    {\it Right:}
    As on the left, with the transit removed.  Quarters 6 and 7 show a
    consistent deviation in the second half of the transit.
		\label{fig:phasequarter}
	}
\end{figure}

@@

Our model therefore included 10 free parameters for the transit ($\{P,
t_0, R_{\rm p}/R_\star, b, u_1 ,u_2 ,R_\star, \log g, e, \omega \}$),
2 free parameters for the light curve normalization and uncertainty
calibration ($\{\langle f \rangle, \sigma_f \}$), and 5
hyperparameters for the GP ($\{\sigma_{\mathrm{rot}},
P_{\mathrm{rot}}, Q_0, \mathrm{d}Q, f \}$).  We also considered
including an additive \texttt{SHOTerm} kernel to account for
stochastic noise, but found that this did not significantly affect the
results, and so opted for the simpler GP kernel.  We fitted the models
using \texttt{PyMC3} \citep{salvatier_2016_PyMC3,exoplanet:theano}.
We assumed a Gaussian likelihood, and after initializing each model
with the parameters of the maximum {\it a posteriori} model, we
sampled using \texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014} in these bases indicated in
Table~\ref{tab:posterior}.  We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.

>>>>

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Further
observations of spectroscopic transits could yield a quantification of
the stellar obliquity, and would confirm or refute the expected
prograde orbital geometry.  Separately, transit spectroscopy aimed at
detecting atmospheric outflows could yield insight into the
evolutionary state of the atmosphere \citep[{\it
e.g.},][]{ehrenreich_giant_2015,spake_helium_2018,vissapragada_2020}.
Observations aimed at quantifying the amount of high-energy
irradiation incident on the planet would complement these efforts, by
helping to clarify the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass.  This might be
possible through a high-cadence multi-color radial velocity campaign,
or through long-term monitoring of the transit times and durations.
Measured at sufficient precision, the mass, combined with the known
age and size, would yield constraints on both the planet's composition
and its initial entropy \citep{owen_constraining_2020}.

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  Other possible explanations such as favored longitudes for
starspot crossings seem strained for reasons discussed in
Appendix~\ref{app:gptransit}.  Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also roughly consistent with predictions
\citep{wang_dai_2019}.  Beyond the planetary transits,
Appendix~\ref{app:flare} highlights a separate oddity in the Kepler
data, in the arrival time distribution of stellar flares.  We
encourage its exploration by investigators more versed in the topic
than ourselves.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.64\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Transit model residuals through time (binned by Kepler quarter)}.  
    {\it Left:}
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  Black points are binned to 20
    minute intervals.  The 2-$\sigma$ model uncertainties and the
    maximum {\it a posteriori} model are shown as the faint purple
    band, and the dark purple line.
    {\it Right:}
    As on the left, with the transit removed.  Quarters 6 and 7 show a
    consistent deviation in the second half of the transit.
		\label{fig:phasequarter}
	}
\end{figure}

@@

Our model therefore included 10 free parameters for the transit ($\{P,
t_0, R_{\rm p}/R_\star, b, u_1 ,u_2 ,R_\star, \log g, e, \omega \}$),
2 free parameters for the light curve normalization and uncertainty
calibration ($\{\langle f \rangle, \sigma_f \}$), and 5
hyperparameters for the GP ($\{\sigma_{\mathrm{rot}},
P_{\mathrm{rot}}, Q_0, \mathrm{d}Q, f \}$).  We also considered
including an additive \texttt{SHOTerm} kernel to account for
stochastic noise, but found that this did not significantly affect the
results, and so opted for the simpler GP kernel.  We fitted the models
using \texttt{PyMC3} \citep{salvatier_2016_PyMC3,exoplanet:theano},
and accounted for the finite integration time of each exposure in the
numerical integration when evaluating the model light curve
\citep[see][]{kipping_binning_2010}.  We assumed a Gaussian
likelihood, and after initializing each model with the parameters of
the maximum {\it a posteriori} model, we sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014} in these bases indicated in
Table~\ref{tab:posterior}.  We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.
